Notes for ISIPTA poster

### 2016-07-07 asce-paper.tex
adding refs, work on intro

\def\Tsys{T_\text{sys}}

@@

In reliability engineering, a central task is to describe the reliability of a complex system.
This is usually done by determining the \emph{reliability function} $R(t)$,
in other contexts also known as the \emph{survival function} $S(t)$,
giving the probability that the system has not failed by time $t$:
\begin{align}
R_\text{sys}(t) = P(T_\text{sys} \geq t)\,,
\end{align}
where $T_\text{sys}$ is the random variable giving the failure time of the system. %
%\footnote{}
Based on the distribution of $T_\text{sys}$, which can also be expressed
in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - R_\text{sys}(t)$,
the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
decisions about, e.g., scheduling of maintenance work can be made.

Often, there is no failure data for the system itself
(e.g., if the system is a prototype, or the system is used under unique circumstances),
but there is some information about failure times for the components the system is made of.
Information on the distribution of component failure times $T_i$,
where $i = 1, \ldots, n$ if the system consists of $n$ components,
can then be used to derive the distribution of $T_\text{sys}$.
In this paper, we consider*** a simple parallel system
where all components are of the same type,
and our observations consist solely of the failure times of one or more components in this system.
%In the last section, we will briefly describe
%how the approach can be generalized to arbitrary system structures
%using the survival signature \cite{2012:survsign},
%which allows for different types of components and
%the inclusion of data from component tests, as in \citeNP{2014:bayessurvsign}.
%
We assume a parametric probability distribution for component lifetimes $T_i$. 
The Bayesian approach allows to base estimation of the component failure distributions
on both data and further knowledge not given by the data,
the latter usually provided in the form of expert knowledge.
This knowledge is encoded in form of a so-called prior distribution,
a distribution on the parameter(s) of the component lifetime distribution.
This expert knowledge is especially important when there is very few data on the components (like in our scenario),
as only with its help meaningful estimates for the system reliability can be made.

@@

System with components of $k=1,\ldots,K$ different types.
There are $n_k$ components of type $k$ in the system.

@@

>>>>

\def\Rsys{R_\text{sys}}
\def\Tsys{T_\text{sys}}

@@

In reliability engineering, a central task is to describe the reliability of a complex system.
This is usually done by determining the \emph{reliability function} $R(t)$,
in other contexts also known as the \emph{survival function} $S(t)$,
giving the probability that the system has not failed by time $t$:
\begin{align}
\Rsys(t) = P(\Tsys \geq t)\,,
\end{align}
where $\Tsys$ is the random variable giving the failure time of the system. %
%\footnote{}
Based on the distribution of $\Tsys$, which can also be expressed
in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
decisions about, e.g., scheduling of maintenance work can be made.

Often, there is no failure data for the system itself
(e.g., if the system is a prototype, or the system is used under unique circumstances),
but there is some information about failure times for the components the system is made of.
We are able to analyse systems of arbitrary system structures, %layout of components,
i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
by use of the survival signature \cite{2012:survsign}.
In this paper, we assume that components can be divided into $K$ different groups,
and components within each group $k$ ($k=1, \ldots, K$) can be assumed to follow the same failure time distribution.
We denote components of group $k$ as \emph{type $k$ components},
and assume independence between component types,
such that failure times of components of different types are independent.
We assume that type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
are Weibull distributed, with type-specific parameters $\beta_k$ (shape) and $\lambda_k$ (scale).
***type-specific shape not implemented yet!***

Focusing on the prototype application,
we assume that our observations consist solely of the failure times of components in this system up to time $\tnow$,
such that the failure times of components that have not failed by $\tnow$ are right-censored,
and calculate $\Rsys(t \mid t > \tnow) = P(\Tsys \geq t \mid t > \tnow)$,
which can be used to determine the remaining useful life (in short RUL, see, e.g., ***) of the system.
%This sparse information is complemented by expert information on component lifetimes $T_i^k$.

The Bayesian approach allows to base estimation of the component failure distributions
on both data and further knowledge not given by the data,
the latter usually provided in the form of expert knowledge.
This knowledge is encoded in form of a so-called prior distribution,
a distribution on the parameter of the component lifetime distributions.
This expert knowledge is especially important when there is very few data on the components (like in our scenario),
as only with its help meaningful estimates for the system reliability can be made.

***

This work extends \ldots

The paper is structured as follows:

%In the last section, we will briefly describe
%how the approach can be generalized to arbitrary system structures
%using the survival signature \cite{2012:survsign},
%which allows for different types of components and
%the inclusion of data from component tests, as in \citeNP{2014:bayessurvsign}.
%Information on the distribution of component failure times $T_i$,
%where $i = 1, \ldots, n$ if the system consists of $n$ components,
%can then be used to derive the distribution of $T_\text{sys}$.

@@

System with components of $k=1,\ldots,K$ different types.
There are $n_k$ exchangeable components of type $k$ in the system.

@@

\pagebreak
%
%
% Now we start the appendices, with the new section name, "Appendix", and a 
%  new counter, "I", "II", etc.
%
\appendix\label{section:references}
%
% Here's the first appendix, the list of references:
%
\bibliography{refs}
%
%\cite{key}   produces citations with full author list and year 
%\citeNP{key} produces citations with full author list and year, but without enclosing parentheses
%\citeA{key}  produces citations with only the full author list
%\citeN{key}  produces citations with the full author list and year, but
%             which can be used as nouns in a sentence; no parentheses appear around
%             the author names, but only around the year
%\citeyear{key}   produces the year information only, within parentheses
%\citeyearNP{key} produces the year information only
%
%
% And now for some pretty impressive notation.  In this example, I have used
%   the tabular environment to line up the columns in ASCE style.
%   Note that this and all appendices (except the references) start with 
%   the \section command
%
\section{Notation}
\emph{The following symbols are used in this paper:}%\par\vspace{0.10in}
\nopagebreak
\par
\begin{tabular}{r  @{\hspace{1em}=\hspace{1em}}  l}
$D$                    & pile diameter (m); \\
$R$                    & distance (m);      and\\
$C_{\mathrm{Oh\;no!}}$ & fudge factor.
\end{tabular}
